On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-05-31 Manuscript/manuscript.tex
Added reaction times table
update before tuesday meeting

\jy{label the table and reference to it; clean it up}
\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than 0.1, 0.08, and
  0.08 for various data sets.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & P(RxnTime $<$ 0.1) & P(RxnTime $<$ 0.08) \\ 
   \midrule
   Old Finals & $4.39\cdot10^{-4}$ & $2.0\cdot10^{-5}$ \\
   All Finals & $8.56\cdot10^{-4}$ & $6.0\cdot10^{-7}$ \\
   Old Pooled & $5.76\cdot10^{-3}$ & $1.0\cdot10^{-4}$ \\ 
   All Pooled & $6.86\cdot10^{-3}$ & $1.3\cdot10^{-4}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on probability of observing
  a time less the barrier. \of{Not sure if this makes sense}}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & P(RxnTime $<$ x = .001) & P(RxnTime $<$ x = 0.0001) \\ 
   \midrule
   Old Finals & $4.39\cdot10^{-4}$ & $2.0\cdot10^{-5}$ \\
   All Finals & $8.56\cdot10^{-4}$ & $6.0\cdot10^{-7}$ \\
   Old Pooled & $5.76\cdot10^{-3}$ & $1.0\cdot10^{-4}$ \\ 
   All Pooled & $6.86\cdot10^{-3}$ & $1.3\cdot10^{-4}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:ExpectedValues}
\end{table}

@@

@@

>>>>

\jy{label the table and reference to it; clean it up}
\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than 0.1, 0.08, and
  0.08 for various data sets.}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ 0.1) & P(RxnTime $<$ 0.08) \\ 
   \midrule
   Old Finals & $4.39\cdot10^{-4}$ & $2.0\cdot10^{-5}$ \\
   All Finals & $8.56\cdot10^{-4}$ & $6.0\cdot10^{-7}$ \\
   Old Pooled & $5.76\cdot10^{-3}$ & $1.0\cdot10^{-4}$ \\ 
   All Pooled & $6.86\cdot10^{-3}$ & $1.3\cdot10^{-4}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on probability of observing
  a time less the barrier. \of{Not sure if this makes sense}}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ x = .001) & P(RxnTime $<$ x = 0.0001) \\ 
   \midrule
   Old Finals & $0.103$ & $0.095$ \\
   All Finals & $0.101$ & $0.093$ \\
   Old Pooled & $0.090$ & $0.080$ \\ 
   All Pooled & $0.089$ & $0.079$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}

@@

We can use the same model but alter our interpretation slightly to select a 
reaction time barrier given the probability of observing a time less than the 
barrier.  For example, if we want a 0.1\% chance of observing an illegally fast 
reaction time for the men's pooled dataset that includes 2022, then the reaction
time barrier should be 0.089 seconds, as shown in Table~\ref{tab:Sim_time}.  We
can repeat this calculation for each dataset and for various probability levels,
for example a probability of 0.0001 (one disqualification for every 10,000 starts)
results in a reaction time barrier of 0.079 for the men's pooled dataset.  
Tables~\ref{tab:Sim_time} shows that the inclusion of 2022 results in a lower
reaction time barrier, further showing the claims above that the reaction times
in 2022 were low.

@@

The rank based methods described in Section~\ref{sec:rank} are used
to determine if the reaction times for athletes who had competed at other 
championships differed significantly from the 2022 World Championships.  We can
use the 2019 World Championships and the 2022 national-level championships as a 
precedent to see how athletes performance changed across different championships.
